Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-09-21 manuscript/manuscript.tex
Move the implementation section to Methodology
The section is small and describes the basis for the method developed,
so it fits in with the methodology. Included a link to the Github repo
(Zenodo DOI will come later).
Removed the details about the Fatiando code using numba. That would be
good on a software paper but not here.

@@

\section{Implementation}

In order to perform the determinations of the distance-size and the
delta ratio, we have developed a Python code that implements the
discretization algorithms and the GLQ to finally compute the
gravitational fields.

It is based on the pre-existing code developed by \citet{Uieda2016} (and
included in Fatiando a Terra v.0.5, \citet{Uieda2013}) that computes
the gravitational effects of tesseroids with homogeneous density.
Our implementation keeps the the homogeneous tesseroid calculation and
the modified adaptive discretization algorithm while incorporates the
new variable density computations with the density-based discretization
algorithm.
On their software, \citet{Uieda2016} have optimised the more time
consuming functions through the Numba compiler.
In contrast, we have decided to develop our new library in Cython
language due to difficulties when passing a Python function as argument
to precompiled Numba methods.

This new code is freely available under the BSD 3-clause open-source
license and makes use of the pre-existing classes and functions of
Fatiando a Terra v0.5 in order to define single tesseroid or meshes of
them.
It can be downloaded from ...
\todo[inline]{include repo url}

>>>>

\subsection{Software implementation}

We have implemented the algorithms described in the previous sections in the Python
programming language.
The software is based on the pre-existing code for the homogeneous density tesseroid
\citep{Uieda2016}, more specifically the implementation in the Python library Fatiando a
Terra v0.5 \citep{Uieda2013}.
The more time consuming parts of the algorithm are written in the Cython language to
achieve higher performance.
This new code is freely available under the BSD 3-clause open-source license.
It can be downloaded from the online repository
\href{https://github.com/pinga-lab/tesseroid-variable-density}{github.com/pinga-lab/tesseroid-variable-density}.

@@
